resistanceModelNotesAndy

### 2015-03-24 resistanceModelNotesAndy.Rmd
progress notes

**23/3/15** tue 9.45-

@@

@@

@@

1. the curtis fig2 plot is produced from >1 scenario, do I want to get it into 1 'reactive' scenario
1. put back in checks for things that should sum to 1
1. edit runModel carefully
1. check out the part about running sequential insecticide scenarios
1. start to write script to run sensitivity analysis, does it want to work by creating a large input.csv file, or by setting input object directly.
1. spend some time developing my understanding of how the model works
1. submit tilde bug report
1. re-look at R popgen packages when I've got more of a handle on what we are doing.

>>>>

**23/3/15** tue 9.45-2.15 4.5hrs

@@

Sent message to Ian & Beth to test installing from Github and the shinyUI.

@@

1. start to write script to run sensitivity analysis, does it want to work by creating a large input.csv file, or by setting input object directly.

1. submit travel claim & maybe first invoice after creating hours spreadsheet

@@

1. the curtis fig2 plot is produced from >1 scenario, do I want to get it into 1 'reactive' scenario
1. edit runModel carefully
1. check out the part about running sequential insecticide scenarios

1. spend some time developing my understanding of how the model works
1. submit tilde bug report
1. re-look at R popgen packages when I've got more of a handle on what we are doing.
